---
title: "OPprob2"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{OPprob2}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


**OPprob2** is a function that finds the Ordinal Patterns probabilities in a time series for a 
given embedding dimension. It is based on the **OPprob** function from the *StatOrdPattHxC* package.
It has been rewritten using Object Oriented Programming and a plotting capability has been added. The
examples below have been borrowed from *StatOrdPattHxC*.


### Arguments 

#### 1. TS (Required)

A time series of length $n − m + 1$.

#### 2. emb (Required)

The embedding dimension m. This is the number of consecutive points that form each ordinal pattern. It must be an integer greater than 1.

#### Returns

A probability function $\boldsymbol{p} = (p_1, p_2, ..., p_{m!})$ 

### Examples


```{r setup, warning=FALSE, echo=FALSE}
library(ordpatt2)
library(ggplot2)
library(ggthemes)
```


```{r, echo=TRUE, eval=TRUE}
set.seed(1234567890, kind="Mersenne-Twister")
x <- rnorm(1000) # white noise
y <- mov.av(x, order=11) # smoothed with moving averages
opx <- OPprob2(x, emb=4)
opy <- OPprob2(y, emb=4)

```


```{r, echo=TRUE, eval=TRUE}
opx
opy
```


```{r, echo=TRUE, eval=TRUE}
plot(opx)
plot(opy)
```




