---
title: "OPseq2"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{OPseq2}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

**OPseq2** is a function that finds the ordinal pattern sequence of a time series, 
given the embedding dimension and lag. It is based on the 
**OPseq** function from the *StatOrdPattHxC* package. It depends on two internal 
subfunctions, **pi_i2** and **perm2**. The original functions **pi_i** and **perm**
from *StatOrdPattHxC* were causing the function to run slowly and have been rewritten
in C++. The examples below have been borrowed from *StatOrdPattHxC*.


### Arguments 

#### 1. TS (Required)

A time series of length $n − m + 1$.

#### 2. emb (Required)

The embedding dimension m. This is the number of consecutive points that form each ordinal pattern. It must be an integer greater than 1.

#### 3. lag (Optional)

The time lag between two time series observations. It must be an integer greater than 0. The default value is 1.

#### Returns

A series of integers indicating the ordinal pattern sequence for that section of the time series.

### Examples



```{r setup, warning=FALSE, echo=FALSE}
library(ordpatt2)
```



```{r, echo=TRUE, eval=TRUE}
# Generate a time series and compute its ordinal patterns
set.seed(1234567890, kind="Mersenne-Twister")
x <- rnorm(1000) # white noise
y <- rnorm(100)
OPseq2(x, emb=4, lag=1)[1:20]
OPseq2(y, emb=3, lag=1)

```
